Figures

### 2020-03-16 figures/07_model-selection.Rmd
rename buffer category to spatial config

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  dplyr::bind_rows(
    dplyr::select(re_global[best_tp,], -term, -response), 
    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
               stringsAsFactors = FALSE)
    ) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer configuration", 
                                        LULC = "Land-use cover")) %>%
  arrange(category) %>%
  ungroup() %>% distinct(pretty, .keep_all = TRUE) %>%
  mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

>>>>

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  dplyr::bind_rows(
    dplyr::select(re_global[best_tp,], -term, -response), 
    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
               stringsAsFactors = FALSE)
    ) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        `Spatial\nconfig.` = "Buffer configuration", 
                                        LULC = "Land-use cover")) %>%
  arrange(category) %>%
  ungroup() %>% distinct(pretty, .keep_all = TRUE) %>%
  mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

### 2020-03-16 figures/07_model-selection_nolulc.Rmd
rename buffer category to spatial config

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer configuration", 
                                        LULC = "Land-use cover")) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)
```

>>>>

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        `Spatial\nconfig.` = "Buffer configuration", 
                                        LULC = "Land-use cover")) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)
```
